\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2018-10-17 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Updated the Astronum_2018 document.

\subsection{Transport Equations}
Considering the neutrino pass through a static dense matter and only emission, absorption and elastic scattering exist, the transport equation of the neutrino after scaling to dimensionless units can be written as
\begin{equation}
  \pd{f}{t}+\vect{\ell}\cdot\nabla f
  =\f{1}{\tau}\,\cC(f),
  \label{eq:boltzmann}
\end{equation}
which is known as Boltzmann equation.
The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrino propagating in the direction $\omega\in\bbS^{2}$, with neutrino energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.  
$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector which parallel to the neutrino three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
On the right-hand side, $\tau$ is interaction strength parameter: $\tau\ll1$ for opaque region where neutrino has strong interaction with the background; $\tau\gg1$ for transparent region where neutrino has weak interaction with the background and streams freely.
$\cC(f)$ is the collision term, which models emission, absorption, and isotropic and elastic scattering: 
\begin{equation}
  \cC(f)=\xi\,\big(\,f_{0}-f\,\big)
  +(1-\xi)\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omega-f\,\big),
  \label{eq:collisionTerm}
\end{equation}
with $\xi = \sigma_{\Ab} / (\sigma_{\Ab}  + \sigma_{\Scatt} )$ be the emission and absorption contribution parameter: $\xi = 1$ when the scattering opacity $\sigma_{\Scatt} = 0$, pure emission and absorption; $\xi = 0$ when the absorption opacity $\sigma_{\Ab} = 0$, pure scattering. 
$f_{0}$ is the neutrino equilibrium distribution function which has the following form:
\begin{equation}
  f_{0}(\vect{z})=\f{1}{e^{(\varepsilon-\mu(\vect{x}))/T(\vect{x})}+1}.
  \label{eq:fermiDirac}
\end{equation}
$T(\vect{x})$ is the temperature in energy unit and $\mu(\vect{x})$ is the neutrino chemical potential.
Both of them depend on the properties of the background as a function of $\vect{x}$.

\subsection{Two-Moment Model}
An approximate solution of Boltzmann equation Eq.~\eqref{eq:boltzmann} can be found by employing two-moment model.
Define the angular moments of the distribution function as following
\begin{equation}
  \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\vect{z},t)
  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega,
  \label{eq:angularMoments}
\end{equation}
where $\vect{z}:=\{\varepsilon,\vect{x}\}$, the zeroth moment $\cJ$ is referred as the particle density, the first moment $\bcH$ is the particle flux, and the second moment $\bcK$ is the stress tensor.
Then integral Eq.~\eqref{eq:boltzmann} as the zeroth and the first moments both side to have
\begin{equation}
  \pd{\vect{\cM}}{t}+\nabla\cdot\vect{\cF}=\f{1}{\tau}\,\vect{\cC}(\vect{\cM}),
  \label{eq:momentEquations}
\end{equation}
with $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, $\vect{\cF}=(\vect{\cH},\vect{\cK})^{T}$, and
\begin{equation}
  \vect{\cC}(\vect{\cM})=\vect{\eta}-\vect{\cD}\,\vect{\cM},
  \label{eq:collisionTermMoments}
\end{equation}
where $\vect{\eta}=(\xi\,f_{0},\vect{0})^{T}$, $\vect{\cD}=\mbox{diag}(\xi,\vect{I})$, and
$\vect{I}$ is the identity matrix.
Therefore, solving Boltzmann equation Eq.~\eqref{eq:boltzmann} for a neutrino distribution function $f(\omega,\vect{z},t)$ is converted to solving two-moment equations for the neutrino number density $\cJ(\vect{z},t)$ and the neutrino flux $\bcH(\vect{z},t)$.

\subsection{Algebraic Closures }
As it shown in previous section, the $i$-th order moment equation requires information of the $(i+1)$-th order moment and leads the two-moment system be open. 
To close the two-moment system, a strategy named algebraic closure is built.
For a two-moment method, algebraic closures give an approximate $\bcK$ based on the lower moments as following:
\begin{equation}
\bcK = \vect{k} \cJ,
\end{equation}
where $\vect{k}$ is the Eddington tensor.
Assume the neutrino transport is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore\cite{levermore_1984} proposed
\begin{equation}
  \vect{k}=\f{1}{2}\big[\,\big(1-\chi\big)\,\vect{I}+\big(3\,\chi-1\big)\,\widehat{\vect{h}}\otimes\widehat{\vect{h}}\,\big],
  \label{eq:eddingtonTensor}
\end{equation}
where $\chi=\chi(\cJ,|\vect{\cH}|)$ is the Eddington factor.

\subsection{Constraints on Moments}
One fundamental fact about neutrino is that they are fermion which follow the Pauli exclusion principle, $f \in (0,1)$.
As a result, the angular moments of $f$ are confined as the following: 
\begin{align}
\cJ \in(0,1), \quad &(1-\cJ)\cJ-|\vect{\cH}|  > 0, \label{eq:MomentsBounds}\\
  \chi_{\mbox{\tiny min}}
  =\max\big(1-\f{2}{3\cJ},h^{2}\big)
  < & \chi<\min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}},
  \label{eq:eddingtonFactorBounds}
\end{align}
where $h = |\bcH|/\cJ$ is the flux factor.[citation]

The inequalities in Eq.\ref{eq:MomentsBounds} define the realizable $\bcM$ which defines a convex set in $\cJ -\bcH$ space.
As we will see later in Section \ref{se:SpacialDiscretization}, this convexity makes a constraint-preserving spacial discretization possible.

The inequalities in Eq.\ref{eq:eddingtonFactorBounds} desire more attention than have be given.
They have the equal importance as the inequalities in Eq.\ref{eq:MomentsBounds} in preserving the validity of the simulation result.
However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.\ref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson1975,leblanc1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka1992} may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1\cite{janka1991} can be dangerous for both the cases. The only algebraic closure that remains in the bounds among those seven plotted closures is Cernohorsky \& Bludman's \cite{cernohorskyBludman_1994}.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_10}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_90}
  \end{tabular}
   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupied) and $\cJ=0.9$ (right panel, high occupied).  In each panel we plot the Eddington factors of Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue) and Janka (purple and pink) closures.  We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dash black lines, respectively).}
  \label{fig:EddingtonFactorsWithDifferentClosure}
\end{figure}

>>>>

\subsection{Transport Equations}
Consider neutrino transport through static dense matter with only emission, absorption and isotropic scattering.
The Boltzmann equation after scaling to dimensionless units ($k_{B} = \hbar = c = 1$) can be written as
\begin{equation}
  \pd{f}{t}+\vect{\ell}\cdot\nabla f
  =\f{1}{\tau}\,\cC(f).
  \label{eq:boltzmann}
\end{equation}
The distribution function $f = f(\omega,\varepsilon,\vect{x},t)$ gives the number of neutrinos propagating in the direction $\omega\in\bbS^{2}$, with neutrino energy $\varepsilon\in\bbR^{+}$, at position $\vect{x}\in\bbR^{3}$ and time $t\in\bbR^{+}$.  
$\vect{\ell} = \vect{\ell}(\omega)\in\bbR^{3}$ is the unit vector parallel to the neutrino three-momentum direction: $\vect{p}=\varepsilon\,\vect{\ell}$.
On the right-hand side, $\tau$ is the interaction strength parameter: $\tau\ll1$ for opaque regions where neutrinos have frequent interactions with the background; $\tau\gg1$ for transparent regions where neutrinos rarely interact with the background and stream freely.
$\cC(f)$ is the collision term, which models emission, absorption, and isotropic and elastic scattering: 
\begin{equation}
  \cC(f)=\xi\,\big(\,f_{0}-f\,\big)
  +(1-\xi)\,\big(\,\f{1}{4\pi}\int_{\bbS^{2}}f\,d\omega-f\,\big),
  \label{eq:collisionTerm}
\end{equation}
with $\xi = \sigma_{\Ab} / (\sigma_{\Ab}  + \sigma_{\Scatt} )$: $\xi = 1$ when the scattering opacity $\sigma_{\Scatt} = 0$ corresponding to pure emission and absorption; $\xi = 0$ when the absorption opacity $\sigma_{\Ab} = 0$ corresponding to pure scattering. 
$f_{0}$ is the neutrino equilibrium distribution function, which has the following form:
\begin{equation}
  f_{0}(\vect{z})=\f{1}{e^{(\varepsilon-\mu(\vect{x}))/T(\vect{x})}+1}.
  \label{eq:fermiDirac}
\end{equation}
$T(\vect{x})$ is the temperature in energy units and $\mu(\vect{x})$ is the neutrino chemical potential.
Both of them depend on the properties of the background as a function of $\vect{x}$.

\subsection{Two-Moment Model}
An approximate solution of the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, can be found by employing a two-moment model.
Define the angular moments of the distribution function as follows
\begin{equation}
  \big\{\,\cJ,\vect{\cH},\vect{\cK}\,\big\}(\vect{z},t)
  =\f{1}{4\pi}\int_{\bbS^{2}}f(\omega,\vect{z},t)\,\{\,1,\vect{\ell},\vect{\ell}\otimes\vect{\ell}\,\}\,d\omega,
  \label{eq:angularMoments}
\end{equation}
where $\vect{z}:=\{\varepsilon,\vect{x}\}$.
The zeroth moment, $\cJ$, is referred to as the particle density.
The first moment, $\bcH$, is the particle flux.
And the second moment, $\bcK$, is the stress tensor.
We can integrate Eq.~\eqref{eq:boltzmann} to their equations of the zeroth and the first moments
\begin{equation}
  \pd{\vect{\cM}}{t}+\nabla\cdot\vect{\cF}=\f{1}{\tau}\,\vect{\cC}(\vect{\cM}),
  \label{eq:momentEquations}
\end{equation}
with $\vect{\cM}=(\cJ,\vect{\cH})^{T}$, $\vect{\cF}=(\vect{\cH},\vect{\cK})^{T}$, and
\begin{equation}
  \vect{\cC}(\vect{\cM})=\vect{\eta}-\vect{\cD}\,\vect{\cM},
  \label{eq:collisionTermMoments}
\end{equation}
where $\vect{\eta}=(\xi\,f_{0},\vect{0})^{T}$, $\vect{\cD}=\mbox{diag}(\xi,\vect{I})$, and
$\vect{I}$ is the identity matrix.
Therefore, solving the Boltzmann equation, Eq.~\eqref{eq:boltzmann}, for the neutrino distribution function, $f(\omega,\vect{z},t)$, is approximated by solving the two-moment equations for the neutrino number density, $\cJ(\vect{z},t)$, and flux, $\bcH(\vect{z},t)$.

\subsection{Algebraic Closures }
As is shown in the previous section, the $i$-th order moment equation requires information of the $(i+1)$-th order moment and the two-moment system is open. 
To close the two-moment system, an algebraic closure is constructed.
For a two-moment method, algebraic closures give an approximate $\bcK$ based on the lower moments as follows:
\begin{equation}
\bcK = \vect{k} \cJ,
\end{equation}
where $\vect{k}$ is the Eddington tensor.
For example, assuming the neutrino transport is symmetric about a preferred direction $\widehat{\vect{h}}=\vect{\cH}/|\vect{\cH}|$, Levermore\cite{levermore_1984} proposed
\begin{equation}
  \vect{k}=\f{1}{2}\big[\,\big(1-\chi\big)\,\vect{I}+\big(3\,\chi-1\big)\,\widehat{\vect{h}}\otimes\widehat{\vect{h}}\,\big],
  \label{eq:eddingtonTensor}
\end{equation}
where $\chi=\chi(\cJ,|\vect{\cH}|)$ is the Eddington factor.

\subsection{Constraints on the Moments}
One fundamental fact about neutrinos is that they are fermions, which obey follow the Pauli exclusion principle, $f \in [0,1]$.
As a result, the angular moments of $f$ are constrained as follows: 
\begin{align}
\cJ \in[0,1], \quad &(1-\cJ)\cJ-|\vect{\cH}|  \geq 0, \label{eq:MomentsBounds}\\
  \chi_{\mbox{\tiny min}}
  =\max\big(1-\f{2}{3\cJ},h^{2}\big)
  \leq & \chi \leq \min\big(1,\f{1}{3\cJ}-\f{\cJ}{1-\cJ}h^{2}\big)=\chi_{\mbox{\tiny max}},
  \label{eq:eddingtonFactorBounds}
\end{align}
where $h = |\bcH|/\cJ$ is the flux factor.\cite{levermore_1984,lareckiBanach_2011,kershaw_1976,shohatTamarkin_1943}

The inequalities in Eq.~\eqref{eq:MomentsBounds} define the realizable $\bcM$, which define a convex set in $\cJ -\bcH$ space.
As we will see later in Section \ref{se:SpacialDiscretization}, this convexity makes a constraint-preserving spatial discretization possible.

The inequalities in Eq.~\eqref{eq:eddingtonFactorBounds} deserve more attention than has been given.
They have equal importance \rc{relative to} the inequalities in Eq.~\eqref{eq:MomentsBounds} in preserving the validity of the simulation result.
However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all algebraic closures satisfy the Eddington factor bounds, Eq.~\eqref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblancWilson_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka_1992} may work fine in the neutrino low occupancy limit, but not for high occupancies; Janka 1\cite{janka_1991} can be in error in both cases.
The only algebraic closure that remains within the Eddington factor bounds among those plotted is Cernohorsky and Bludman's \cite{cernohorskyBludman_1994}.

Though Levermore closure and Minerbo closure don't conserve the bounds in the high occupancy limit, they are widely used: {O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018}, and Just et al\cite{just_etal_2018} use Minerbo closure, and Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018}, and Kuroda et al\cite{kuroda_etal_2016} use Levermore clsoure.

\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_10}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_90}
  \end{tabular}
   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupancy) and $\cJ=0.9$ (right panel, high occupancy).  In each panel we plot the Eddington factors of Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue) and Janka (purple and pink) closures.  We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$, defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dashed black lines, respectively).}
  \label{fig:EddingtonFactorsWithDifferentClosure}
\end{figure}

### 2018-10-17 Documents/M1/Astronum_2018/sections/intro.tex
Updated the Astronum_2018 document.

Core-collapse supernovae (CCSNe) are the explosion of massive stars which end their life.
CCSNe are a dominant source of heavy elements and play an important role in many astrophysical phenomena, such as neutron star and black hole formation.  
Furthermore, these explosions occur at energies and densities relevant to address fundamental questions in nuclear, particle, and gravitational physics. 
A solid theoretical framework for these explosion mechanism will illuminate explanations to many import questions in fundamental physics.

One essential part of the explosion mechanism is neutrino transport which drives the explosion.  
Neutrino transport is modeled by Boltzmann transport equation which is partial differential equation evolving a phase space distribution function $f$.
Simulating the neutrino transport is convert to find a solution of Boltzmann transport equation for a interested domain and period with an acceptable accuracy.

Nevertheless, solving multi-dimensional Boltzmann transport equation can be expensive.
To balance physical fidelity and computational expediency, an approximation method called two-moment method is established.
In two-moment method, the evolve variables are the zeroth and first angular moments of the distribution function $f$, the spectral particle density $\cJ$ and flux $\bcH$ respectively.
However, the Boltzmann transport equation is a nonlinear equation.
Its integral form which gives the two-moment method requires the information of the second angular moment $\bcK$ to close the system.
Therefore, a algebraic closure which gives a approximated value of $\bcK$ given $\cJ$ and $\bcH$ is needed.
The two-moment method has been widely applied with different algebraic closures, such as the Minerbo\cite{minerbo_1978} closure(e.g.~{O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan and et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018} and Just et al\cite{just_etal_2018} ) and the Levermore\cite{levermore_1984} closure(e.g.~Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018} and Kuroda et al\cite{kuroda_etal_2016}).

Applying two-moment method only is not sufficient to have an affordable solution since the simulating period is long considering the physics it involves.
To be precisely, neutrino interact with the background rapidly and its characteristic time scalar is very small comparing to the length of CCSNe explosion process. 
This makes the time step needed by an explicit time integrator small and a lot of calculation needed. 
On the other hand, solving the moment equations fully implicitly requires inverting many band structure matrices whose sizes depend on the space discretization.
The band structure of the large matrices makes not only the matrices inverting expensive but also the simulation parallel unfriendly.
To manipulate these challenges, implicit-explicit (IMEX) methods are taken into consideration.
By treating the transport term explicitly and the collision term implicitly, IMEX methods subject only to a time step governed by the explicit transport term and the matrix it needs to invert is block diagonal dominated.
Therefore, IMEX methods need less step and the calculation for each step is parallelable.

%\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.} 
To employing IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac statistics satisfied algebraic closure for closing the two-moment equations and a convex-invariant diffusion accurate IMEX schemes for ensure a valid result.
Because the angular moments are confined.
Since a neutrino distribution function is confined ($f\in(0,1)$) by the Pauli exclusion principle, its moments as integrals of a confined function over confined domain ($\omega\in\bbS^{2}$) are also confined.
We call the moments satisfying a Fermi-Dirac statistics realizable moments.
Hence, the algebraic closure should give a realizable $\bcK$ and the well-posedness of closure requires realizable $\cJ$ and $\bcH$.
That's why a Fermi-Dirac statistics satisfied algebraic closure is needed.
Then, the realizability of $\cJ$ and $\bcH$ on each time step requires a convex-invariant IMEX.
Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX for two-moment neutrino transport method.
What's more, the physics of neutrino transport in CCSNe requires the IMEX be diffusion limit accurate.

\rc{\cite{gottlieb_etal_2001} showed standard IMEX scheme can't have an order higher than first without a restrict time step requirement.}
To have second-order (or higher-order) accuracy, some correction steps are needed.
Unfortunately, the correction step can deteriorate the accuracy of the IMEX in the diffusion limit and restrict the time step.
To keep simple, we focus on the IMEX scheme without correction step and require it high-order (second or higher order) in the streaming limit and diffusion accurate.
We call these IMEX scheme PD-ARS.
The study of moment realizability and constraint-preserving diffusion accurate IMEX scheme motivates this work.

This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and the constraints on the moments and algebraic closures imposed by Fermi-Dirac statistics;
Section~\ref{se:SpacialDiscretization} gives a first-order finite volume spatial discretization and shows how the spatial discretization preserve constraints in a IMEX step;
Section~\ref{se:TimeIntegration} discusses how to use convex combination to construct PD-ARS and two PD-ARSs, one has second-order in the streaming limit and the other has third-order, are provided;
Section~\ref{se:NumericalTests} presents the results of the numerical tests which demonstrate the portieres of the PD-ARSs; Section~\ref{se:Conclusion} summaries the achievement of this paper.

>>>>

Core-collapse supernovae (CCSNe) are the explosions of massive stars that end their lives.
CCSNe are a dominant source of heavy elements and play an important role in many astrophysical phenomena, such as neutron star and black hole formation.  
Furthermore, these explosions occur at energies and densities relevant to address fundamental questions in nuclear, particle, and gravitational physics. 
A solid theoretical framework for the explosion mechanism will illuminate approaches to many import questions in fundamental physics.

One essential part of the explosion mechanism is neutrino transport, which drives the explosion.  
Ideally neutrino transport would be modeled by the Boltzmann transport equation, which is a partial differential equation evolving a phase-space distribution function $f$.
Simulating the neutrino transport is equivalent to finding a solution of the Boltzmann equation for a specific domain and period with acceptable accuracy.

However, solving the multi-dimensional Boltzmann transport equation is expensive.
To balance physical fidelity and computational expediency, an approximate method called the two-moment method has been adopted.
In the two-moment method, the evolved variables are the zeroth and first angular moments of the distribution function $f$: the spectral particle density $\cJ$ and flux $\bcH$, respectively.
However, the Boltzmann transport equation is a nonlinear equation.
Its integral form, which gives the two-moment method system of equations, requires knowledge of the second angular moment $\bcK$ to close this system.
Therefore, an algebraic closure that gives an approximate value of $\bcK$ given $\cJ$ and $\bcH$ is needed.
The two-moment method has been widely applied with different algebraic closures, such as the Minerbo\cite{minerbo_1978} closure(e.g.~{O'Connor} and {Couch}\cite{oConnorCouch_2018}, Pan and et al\cite{pan_etal_2018}, Glas et al\cite{glas_etal_2018}, and Just et al\cite{just_etal_2018} ) and the Levermore\cite{levermore_1984} closure(e.g.~Vartanyan et al\cite{vartanyan_etal_2018}, Cabezon et al\cite{cabezon_etal_2018}, and Kuroda et al\cite{kuroda_etal_2016}).

Applying the two-moment method alone does not guarantee an affordable solution.
To be precise, neutrinos interact with the background, and the characteristic time scale of these interactions are very small compared to the domination of the CCSN explosion. 
This makes the time step needed by an explicit time integrator prohibitively small. 
On the other hand, solving the moment equations fully implicitly requires inverting globally many band-structured matrices whose sizes depend on the spatial discretization.
Such a global inversion is both expensive and parallelization unfriendly.
To circumvent these challenges, implicit-explicit (IMEX) methods are taken into consideration.
By treating the transport terms in the two-moment equations explicitly and the collision terms implicitly, IMEX methods are subject only to a time step governed by the explicit transport terms, and the matrices to be inverted are block diagonal dominated.
Therefore, IMEX methods require fewer time steps, and the calculation for each step is parallelizable.

%\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.} 
To employ IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac-statistics-preserving algebraic closure for closing the two-moment equations and a convex-invariant, diffusion-accurate IMEX scheme to ensure a physical result.
Because the angular moments are confined.
Since the neutrino distribution function is constrained ($f\in[0,1]$) by the Pauli exclusion principle, its moments as integrals of a constrained function over constrained domain ($\omega\in\bbS^{2}$) are also constrained.
We call the moments satisfying Fermi-Dirac statistics \textit{realizable moments}.
Hence, the algebraic closure should give a realizable $\bcK$, and the well-posedness of closure requires realizable $\cJ$ and $\bcH$.
That's why a Fermi-Dirac statistics satisfied algebraic closure is needed.
Then, the realizability of $\cJ$ and $\bcH$ on each time step requires a convex-invariant IMEX scheme.
Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX scheme for two-moment neutrino transport.
What's more, the physics of neutrino transport in CCSN requires the IMEX scheme to be diffusion-accurate.

\cite{gottlieb_etal_2001} showed standard IMEX scheme can't have an order higher than first without a restrict time step requirement.
To have second-order (or higher-order) accuracy, some correction steps are needed.
Unfortunately, the correction steps can deteriorate the accuracy of the IMEX scheme in the diffusion limit and restrict the time step.
To keep things simple, we focus on IMEX schemes without correction steps and require them to be high-order (second or higher order) in the streaming limit and diffusion-accurate.
We call these IMEX schemes \textit{PD-ARS}.
The study of moment realizability and constraint-preserving, diffusion-accurate IMEX schemes motivate this work.

This paper is organized as follows: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and the constraints on the moments and algebraic closures imposed by Fermi-Dirac statistics;
Section~\ref{se:SpacialDiscretization} gives a first-order finite-volume spatial discretization and shows how the spatial discretization preserves constraints in an IMEX step;
Section~\ref{se:TimeIntegration} discusses how to use convex combination to construct PD-ARS scheme and two PD-ARS schemes, one with second-order accuracy in the streaming limit and the other with third-order accuracy in the same limit;
Section~\ref{se:NumericalTests} presents the results of the numerical tests, which demonstrate the properties of the PD-ARS schemes; Section~\ref{se:Conclusion} summarizes the achievements of this paper.
